---
title: "Survey_analysis"
author: "Jung Mee Park"
date: "10/21/2021"
output: html_document
---
### the above is a yml stub. 
### https://www.markdownguide.org/cheat-sheet/

## Purpose
The purpose of this report is to overview the data for **Fall 2021 survey**. 

You can create lists in R markdown. 
unordered: 
* redo markdown
* do a violin plot

ordered: 
1. load [data](url here)
2. clean data in time series
3. make plot

#High Level Analysis Plan:
1.     Generate straight frequencies and percentages for each question and response
2.     Break down responses by
a.     Respondent college (if ns are big enough) (Primary_Department__r.Name)
 i.     If that is too fine grained, use Parent_Organization__c
b.     By products used (counter.Scheduling/Notes, counter. Service Desk, counter.Events, Counter.Marketing – SF)
 i.     If per product is too fine grained, try Profile.Name
c.     By time using Trellis
 i.     Break into chunks based on user creation date (CreatedDate)
1.     <1 month
2.     1-6 months
3.     6 months to a year
4.     1 year+
3.     Compare the invited list to respondents on the above criteria to see if there is better respondent representation across some groups.

# literate programming approach like a Jupyter Notebook. 
Rmarkdown automatically creates reports. 
You can automatically update your Rmarkdown when data is updated. 
# where did they stop off with the survey
Use the Progress variable

mean time in seconds for incomplete surveys is 16056.78.
mean time in seconds for completed surveys is 28547.17.

```{r, message=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(magrittr)
library(tidyr)
library(forcats)
library(lubridate)
library(dplyr)
library(knitr)
library(lattice)
library(likert)
library(MASS)
library(psych)
library(viridis)
library(here)
library(flextable)
library(devtools)
```


quantiles
```{r}
quant_time <- tapply(fall_survey$Duration..in.seconds., fall_survey$Finished, quantile)
quant_time
```
or just the summary 
```{r}
# sum_time <- tapply(fall_survey$Duration..in.seconds., fall_survey$Finished, summary)
# sum_time
```

# completed surveys
There were 239 surveys returned and 198 were completed. 

# creating date intervals
2021-10-01 was when the last survey was turned in 

Respondent college 
```{r}
# overview_pct1 <- fall_survey %>% 
#   group_by(Parent_Organization__c) %>% 
#   summarize(count = n()) %>%  # count records by species
#   mutate(pct = count/sum(count))
# 
# pct_graph1 <- 
#   ggplot(overview_pct1, aes(Parent_Organization__c, 
#                            count, fill = Parent_Organization__c)) +
#   geom_bar(stat='identity') +
#   labs(x = "Units", y = "Respondents") +
#   coord_flip() +
#   theme(legend.position="none") +
#   geom_text(aes(label = scales::percent(pct), y = if_else(count > 0.1*max(count), count/2, count+ 0.05*max(count))))
# 
# pct_graph1 <- pct_graph1 + labs(title = "Respondents across parent organizations", 
#                               subtitle = "full data",  fill = "Department Name")
# 
# print(pct_graph1)

```
easier as a table
```{r}
#
```


```{r}
# table(fall_survey$Parent_Organization__c)
```


```{r}
```
For question 3 
```{r}
q3_plot <- plot(likert(fall_survey[,18:21]), ordered = F, wrap= 40) # this looks good. but add more to it.
q3_plot <- q3_plot + labs(title = "Interactions with Trellis staff",
                          subtitle = "Question 3 - full data")

print(q3_plot)

```
question 4 graph
```{r}
Q4graph <- fall_survey %>%
  group_by(Profile.Name) %>% 
  # mutate(Q4 = fct_infreq(Q4)) %>%
  drop_na(Q4) %>% 
  ggplot(aes(x = factor(Q4)), y = ..count.., fill = Profile.Name) +
  geom_bar(aes(fill = Profile.Name)) +
  coord_flip() +
  labs(x = "", y = "responses")

Q4graph <- Q4graph + labs(title = "How satisfied were you with your initial training in Trellis?",
                          subtitle = "Question 4 based on profile name", fill = "Profile Name")

print(Q4graph)
```

Question 6 
```{r}
q6_plot <- plot(likert(fall_survey[,23:25]), ordered = T, wrap= 40) # this looks good. but add more to it. 

q6_plot <- q6_plot + labs(title = "Suport for and knowledge of Trellis",
                            subtitle = "Question 6 - full data") 

print(q6_plot)
```

Question 7 
```{r}
Q7_pct <- long_Q7 %>% 
  group_by(response) %>%
  summarize(count = n()) %>%  # count records by species
  mutate(pct = count/sum(count))

table(long_Q7$response)
```

graph of Q7 
```{r}
Q7graph <- 
  ggplot(Q7_pct, aes(response,count, fill = response)) +
  geom_bar(stat='identity') +
  labs(x = "", y = "") +
  # coord_flip() +
  theme(legend.position="none") +
  geom_text(aes(label = scales::percent(pct), y = if_else(count > 0.1*max(count), count/2, count+ 0.05*max(count))))

Q7graph <- Q7graph + labs(title = "Which of these tools do you use to get help with Trellis?",
                          subtitle = "Question 7 - full data") + 
                          theme(legend.position="none")

print(Q7graph)

```
question 9 
```{r}
q9_plot <- plot(likert(fall_survey[,32:35]), ordered = F, wrap= 40) # this looks good. but add more to it. 
q9_plot <- q9_plot + labs(title = "Ease of Trellis",
                            subtitle = "Question 9 - full data") 

print(q9_plot)
```
question 11
```{r}
q11_plot <- plot(likert(fall_survey[,36:38]), ordered = F, wrap= 40) # this looks good. but add more to it. 
q11_plot <- q11_plot + labs(title = "Benefits of Trellis",
                          subtitle = "Question 11 - full data") 

print(q11_plot)
```
There are really only 3 user groups. Most are in the over 1 year of use category. So you expect some flexibility. 

re-evaluate some stuff like q4 and q7

Question 7 with period
```{r}
Q7graph <- fall_survey %>% 
  # group_by(period) %>% 
  pivot_longer(Q7_1:Q7_6, names_to = "question", values_to = "response", 
               values_drop_na = TRUE) %>%
  ggplot(aes(x = response, fill = period)) +
  geom_bar(aes(fill = period)) +
  coord_flip()+
  # geom_text(stat="count", aes(label=..count..), vjust=1, hjust=1) +
  # # geom_text(stat='count', aes(label = ..count..), position = position_stack(vjust = 0.5)) +
  # geom_boxplot() +
  labs(x = "response", y = "number of respondents") 
  # theme(legend.position=element_blank())
  # geom_text(aes(label = scales::percent(pct), y = if_else(count > 0.1*max(count), count/2, count+ 0.05*max(count))))


Q7graph <- Q7graph + labs(title = "Which of these tools do you use to get help with Trellis?",
                          subtitle = "Question 7 - full data", fill = "User Created Date") + 
                          scale_fill_brewer(palette = "Dark2")

print(Q7graph)

```
breakdown of profile name and time period 
```{r}
## breakdown of user created date and profile name
user_graph <- fall_survey %>%
  group_by(Profile.Name) %>% 
  drop_na(period) %>% 
  ggplot(aes(x = period, y = ..count.., fill = Profile.Name)) +
  geom_bar(aes(fill = Profile.Name)) +
  # coord_flip() +
  labs(x = "", y = "responses")

user_graph <- user_graph + labs(title = "Breakdown of users based on experience",
                          subtitle = "full data", fill = "Profile Name")

print(user_graph)

```

Who dropped out of the survey? 
```{r}
fall_survey$Progress_factor <- as.factor(fall_survey$Progress)

table(fall_survey$Progress_factor)
```

31 left after just filling out their name and did not answer any questions. 
1 left after Q3_2
8 left after Q4
1 left after Q9_4
198 was full complete


As for counter events there were 12 for events, 43 for marketing, 185 for scheduling notes, and 65 for service desk.